Cognitive and Auditory Predictors of Dysarthric Speech Understanding in Older

### 2023-12-21 Manuscript Analyses/manuscript_analysis.Rmd
Intelligibility summary stats

# Intelligibiltiy Descriptives Table

>>>>

# Intelligibility Descriptives Table

speaker_intel <- pl_int %>%
  dplyr::mutate(type = as.factor(type),
                type = fct_relevel(type, "pretest", "posttest")) %>%
  dplyr::group_by(speaker, type) %>%
  dplyr::summarize(pwc = mean(mean_pwc),
                   sd = sd(mean_pwc)) %>%
  dplyr::ungroup() %>%
  tidyr::pivot_wider(names_from = speaker,
                     values_from = c(pwc:sd)) %>%
  dplyr::relocate(sd_AM1, .after = pwc_AM1) %>%
  gt::gt() %>%
    fmt_number(columns = "pwc_AM1":"sd_PDM10", decimals = 2) %>%
    tab_spanner(label = "AM1",
                columns = c(pwc_AM1, sd_AM1)) %>%
    tab_spanner(label = "PDM10",
                columns = c(pwc_PDM10, sd_PDM10)) %>%
    cols_label(type = " ",
               pwc_AM1 = "Mean",
               sd_AM1 = "SD",
               pwc_PDM10 = "Mean",
               sd_PDM10 = "SD")

speaker_intel

speaker_intel %>%
  gt::gtsave("Tables/intel_des.html")
